Figures and supplemental figures for ecological resilience ms

### 2023-12-21 ms_figures_supp_figs.qmd
prep before push to gh repo

# Load project functions
source("R/functions.R")
source("R/fig_functions.R")

@@

# A total of 25 (2023/11/08) simulations were run for each paramter set
# This set allows us to determine the number of simulations to use 
# in the contour plots to produce clear contours by picking a random subset of
# simulations up to the full set of simulations

@@

@@

fig3 <- plot_grid(p1, p2, labels = letters[1:2], label_size = 9, byrow = FALSE)

ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.png", 
       plot = fig3, 
       height = 8, width = 5)
ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.svg", 
       plot = fig3, 
       height = 8, width = 5)

# ggsave(filename = "output/tmp_figs/fig3-yield.png", plot = p1)
# ggsave(filename = "output/tmp_figs/fig3-biomass.png", plot = p2)
# 
# ggsave(filename = "output/tmp_figs/fig3-yield.svg", plot = p1)
# ggsave(filename = "output/tmp_figs/fig3-biomass.svg", plot = p2)

```{r}
out_fs %>%
  group_by(sim_num, reserve_frac, f_fmsy, year) %>%
  summarize(
    ann_yield = sum(yield, na.rm = TRUE),
    ann_biomass = sum(biomass_at_age, na.rm = TRUE)
  ) %>%
  filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
  ggplot(., aes(x = year, y = ann_biomass)) +
  geom_line() +
  facet_grid(f_fmsy ~ sim_num)

out_fs %>%
  group_by(sim_num, reserve_frac, f_fmsy, year) %>%
  summarize(
    ann_yield = sum(yield, na.rm = TRUE),
    ann_biomass = sum(biomass_at_age, na.rm = TRUE)
  ) %>%
 filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
  ungroup() %>%
  ggplot(., aes(x = year, y = ann_yield)) +
  geom_line() +
  facet_grid(f_fmsy ~ sim_num)

out_fs %>%
    group_by(sim_num, reserve_frac, f_fmsy, year) %>%
    summarize(
        ann_yield = sum(yield, na.rm = TRUE),
        ann_biomass = sum(biomass_at_age, na.rm = TRUE)
    ) %>%
    # filter(near(f_fmsy, 1) | near(f_fmsy, 0.52) | near(f_fmsy, 2.09),  near(as.numeric(reserve_frac), 0)) %>%
    ungroup() %>%
  group_by(sim_num, f_fmsy) %>%
  summarize(med_ann_yield = median(ann_yield)) %>%
  ggplot(., aes(x = f_fmsy, y = med_ann_yield)) +
  geom_line() +
  facet_grid(sim_num ~ .)

@@

@@

fig4 <- plot_grid(p1, p2, labels = letters[1:2], label_size = 9, byrow = FALSE)

ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.png", 
       plot = fig4, 
       height = 8, width = 5)
ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.svg", 
       plot = fig4, 
       height = 8, width = 5)

# ggsave(filename = "output/tmp_figs/fig4-yield.png", plot = p1)
# ggsave(filename = "output/tmp_figs/fig4-biomass.png", plot = p2)
# 
# ggsave(filename = "output/tmp_figs/fig4-yield.svg", plot = p1)
# ggsave(filename = "output/tmp_figs/fig4-biomass.svg", plot = p2)

@@

#| label: boneyard
prep_ann_yield_abund_for_plot <- function(df_out_fs,
                                          frac_reserves = c(0, 0.25, 0.50),
                                          f_fmsys = c(0, 0.52, 1.00, 2.09)) {

  sim_num_2_use <- min(df_out_fs$sim_num)
  if (length(f_fmsys) < 1 | is.null(f_fmsys)) {
    stop("Please specify f_fmsy values to use")
  }

  if (length(frac_reserves) < 1 | is.null(frac_reserves)) {
    stop("Please specify frac_reserves values to use")
  }

    # make a sub function

    return(list(main_plt_df, supp_plt_df, med_yield))
  }
```

Contour plots showing the buffering effects of harvest rate and marine reserves on the abundance of a fished population, when the fished and reserve patches share a larval pool.

```{r}
#| label: figure_4
```

@@

# brf_mei_lp_nice[[2]]
# brf_mei_lp_nice[[1]]
# brf_mei_lp_nice[[3]]

@@

text <- TRUE
# x_text_val <- 550
x_min <- 500
x_max <- 635
x_text_val <- (x_max) - (x_max - x_min)/2

@@

# u_f_fmsys <- u_f_fmsys[u_f_fmsys_ind]

### FUNCTION
quants_df <- bio_yield_df %>%
  dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
  dplyr::summarize(annual_yield = sum(yield),
                   annual_biomass = sum(biomass_at_age)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(sim_num, reserve_frac, f_fmsy) %>%
  dplyr::summarize(
    quant_80_bio = quantile(annual_biomass, 0.8),
    quant_20_bio = quantile(annual_biomass, 0.2),
    quant_80_yld = quantile(annual_yield, 0.8),
    quant_20_yld = quantile(annual_yield, 0.2)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(reserve_frac, f_fmsy) %>%
  dplyr::summarize(
    quant_80_mean_bio = mean(quant_80_bio),
    quant_20_mean_bio = mean(quant_20_bio),
    quant_80_mean_yld = mean(quant_80_yld),
    quant_20_mean_yld = mean(quant_20_yld)
  ) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(reserve_frac = as.numeric(reserve_frac)) %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = reserve_frac, tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`))

### FUNCTION
bio_yield_sel_df <- bio_yield_df %>%
  dplyr::mutate(reserve_frac = as.numeric(reserve_frac),
                year = year - 500) %>%
  dplyr::filter(sim_num == sim_2_use) %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = reserve_frac, tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`)) %>%
  dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
  dplyr::summarize(annual_biomass = sum(biomass_at_age),
                   annual_yield = sum(yield)) %>%
  dplyr::ungroup()

### FUNCTION
biom_ts_plt <- ggplot(
  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
  aes(x = year, y = annual_biomass)
) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  geom_ribbon(aes(
    ymin = biomass_thresh,
    ymax = pmin(annual_biomass, biomass_thresh),
    fill = "Biomass lower"
  )) +
  geom_ribbon(aes(
    ymin = annual_biomass,
    ymax = pmin(annual_biomass, biomass_thresh),
    fill = "Biomass higher"
  )) +
  geom_line(colour = "black") +
    geom_segment(aes(x = 1, y = biomass_thresh, 
                     xend = 135, yend = biomass_thresh),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 11000,
  #   aes(label = mean_biomass_lab)
  # ) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 12500,
  #   aes(label = sd_biomass_lab)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 14000,
#   aes(label = yrs_below_thresh)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 9500,
#   aes(label = cv_biomass_lab)
# ) +
labs(fill = "Above/Below Biomass threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  ylab("Biomass (metric tons)") +
  ylim(0, NA) +
  labs(colour = "Reserve\nfraction") +
  theme_minimal() +
  # geom_hline(data = quants_df, aes(yintercept = quant_80_mean_bio), colour = "orange", linewidth = 1.1, linetype = 1) +
  # geom_hline(data = quants_df, aes(yintercept = quant_20_mean_bio), colour = "orange", linewidth = 1.1, linetype = 1) +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  )

#### ?? FUNCTION: YIELD VERSION
yld_ts_plt <- bio_yield_sel_df %>%
  dplyr::filter(f_fmsy != 0) %>%
  ggplot(data = ., aes(x = year, y = annual_yield)) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  geom_ribbon(aes(
    ymin = yield_thresh,
    ymax = pmin(annual_yield, yield_thresh),
    fill = "Yield lower"
  )) +
  geom_ribbon(aes(
    ymin = annual_yield,
    ymax = pmin(annual_yield, yield_thresh),
    fill = "Yield higher"
  )) +
  geom_line(colour = "black") +
  geom_segment(aes(x = 1, y = yield_thresh, 
                     xend = 135, yend = yield_thresh),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 11000,
  #   aes(label = mean_biomass_lab)
  # ) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 12500,
  #   aes(label = sd_biomass_lab)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 14000,
#   aes(label = yrs_below_thresh)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 9500,
#   aes(label = cv_biomass_lab)
# ) +
labs(fill = "Above/Below Yield threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  ylab("Yield (metric tons)") +
  ylim(0, NA) +
  labs(colour = "Reserve\nfraction") +
  theme_minimal() +
  # geom_hline(data = quants_df %>% dplyr::filter(f_fmsy != 0), aes(yintercept = quant_80_mean_yld), colour = "orange", linewidth = 1.1, linetype = 1) +
  # geom_hline(data = quants_df %>% dplyr::filter(f_fmsy != 0), aes(yintercept = quant_20_mean_yld), colour = "orange", linewidth = 1.1, linetype = 1) +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank()
  )
# }

@@

@@

med_biomass <- get_median_biomass(input_df = out_fs, 
                                  age_mat = sim_species_parms$`Blue rockfish`$A_mat)

# White
# No dispersal
chr_nd_white_med_biomass <- get_median_biomass(input_df = chr_nd_white_out_fs, 
                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
chr_nd_white_med_biomass
cab_nd_white_med_biomass <- get_median_biomass(input_df = cab_nd_white_out_fs, 
                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
cab_nd_white_med_biomass
# larval pool dispersal 
chr_lp_white_med_biomass <- get_median_biomass(input_df = chr_lp_white_out_fs, 
                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
chr_lp_white_med_biomass
cab_lp_white_med_biomass <- get_median_biomass(input_df = cab_lp_white_out_fs, 
                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
cab_lp_white_med_biomass

# ENSO
# No dispersal
chr_nd_mei_med_biomass <- get_median_biomass(input_df = chr_nd_mei_out_fs, 
                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
chr_nd_mei_med_biomass
cab_nd_mei_med_biomass <- get_median_biomass(input_df = cab_nd_mei_out_fs, 
                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
cab_nd_mei_med_biomass
# larval pool dispersal
chr_lp_mei_med_biomass <- get_median_biomass(input_df = chr_lp_mei_out_fs, 
                                  age_mat = sim_species_parms$`China rockfish`$A_mat) 
chr_lp_mei_med_biomass
cab_lp_mei_med_biomass <- get_median_biomass(input_df = cab_lp_mei_out_fs, 
                                  age_mat = sim_species_parms$`Cabezon`$A_mat) 
cab_lp_mei_med_biomass

@@

chr_nd_white_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_white_out_fs,
                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
cab_nd_white_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_white_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
chr_lp_white_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_white_out_fs,
                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
cab_lp_white_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_white_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
chr_nd_mei_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_mei_out_fs,
                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
cab_nd_mei_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_mei_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)
chr_lp_mei_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_mei_out_fs,
                                     age_mat = sim_species_parms$`China rockfish`$A_mat)
cab_lp_mei_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_mei_out_fs, age_mat = sim_species_parms$`Cabezon`$A_mat)

>>>>

# Load project functions
source("R/functions.R")
# source("R/fig_functions.R")

@@

# A total of 5 (2023/12/20) simulations were run for each paramter set
# This set allows us to determine the number of simulations to use 
# in the contour plots to produce clear contours by picking a random subset of
# simulations up to the full set of simulations

@@

F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
                                         fleps_2_fs = spec_fleps_2_fs)
# F_brf_maxes_yield

out_fs <- df_add_fs_out(
  input_df = sim_res_out,
  spec_fleps_2_fs = spec_fleps_2_fs,
  F_maxes_yield = F_brf_maxes_yield,
  waa_g_df = brf_waa_g_df
)
# out_fs

med_yield <- get_median_yield(input_df = out_fs) 
# med_yield

med_biomass <- get_median_biomass(input_df = out_fs)
# med_biomass

out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs)

sum_stats_f_frac_df <-
  summary_stats_by_f_frac(
    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
    median_yield = med_yield,
    median_biomass = med_biomass
  )
# sum_stats_f_frac_df

@@

fig3 <-
  plot_grid(
    p1,
    p2,
    labels = letters[1:2],
    label_size = 9,
    byrow = TRUE,
    nrow = 2,
    ncol = 1
  )

ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.png", 
       plot = fig3, 
       height = 10,
       width = 8)
ggsave(filename = "output/tmp_figs/fig3-brf-nd-mei-biomass-yield.svg", 
       plot = fig3, 
       height = 10,
       width = 8)

@@

med_biomass <- get_median_biomass(input_df = out_fs)
med_biomass

out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs)

@@

fig4 <-
  plot_grid(
    p1,
    p2,
    labels = letters[1:2],
    label_size = 9,
    byrow = TRUE,
    nrow = 2,
    ncol = 1
  )

ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.png", 
       plot = fig4, 
       height = 10,
       width = 8)
ggsave(filename = "output/tmp_figs/fig4-brf-lp-biomass-yield.svg", 
       plot = fig4, 
       height = 10,
       width = 8)

@@

@@

@@

text <- TRUE
# x_text_val <- 550
x_min <- 1
x_max <- 135
x_text_val <- (x_max) - (x_max - x_min)/2

@@

### FUNCTION
bio_yield_sel_df <- bio_yield_df %>%
  dplyr::mutate(reserve_frac = as.numeric(reserve_frac),
                year = year - 500) %>%
  dplyr::filter(sim_num == sim_2_use) %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = reserve_frac, tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`)) %>%
  dplyr::group_by(sim_num, reserve_frac, f_fmsy, year) %>%
  dplyr::summarize(annual_biomass = sum(biomass_at_age),
                   annual_yield = sum(yield),
                   rel_annual_biomass = sum(biomass_at_age) / med_biomass,
                   rel_annual_yield = sum(yield) / med_yield) %>%
  dplyr::ungroup()

### Biomass
biom_ts_plt <- ggplot(
  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
  aes(x = year, y = rel_annual_biomass)
  # aes(x = year, y = annual_biomass)
) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  # geom_ribbon(aes(
  #   ymin = biomass_thresh,
  #   ymax = pmin(annual_biomass, biomass_thresh),
  #   fill = "Biomass lower"
  # )) +
    geom_ribbon(aes(
    ymin = 1,
    ymax = pmin(rel_annual_biomass, 1),
    fill = "Biomass lower"
  )) +
  # geom_ribbon(aes(
  #   ymin = annual_biomass,
  #   ymax = pmin(annual_biomass, biomass_thresh),
  #   fill = "Biomass higher"
  # )) +
    geom_ribbon(aes(
    ymin = rel_annual_biomass,
    ymax = pmin(rel_annual_biomass, 1),
    fill = "Biomass higher"
  )) +
  geom_line(colour = "black") +
    geom_segment(aes(x = 1, y = 1, 
                     xend = 135, yend = 1),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 11000,
  #   aes(label = mean_biomass_lab)
  # ) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 12500,
  #   aes(label = sd_biomass_lab)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 14000,
#   aes(label = yrs_below_thresh)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 9500,
#   aes(label = cv_biomass_lab)
# ) +
labs(fill = "Above/Below Biomass threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  # ylab("Biomass (metric tons)") +
  ylab("Relative Biomass") +
  ylim(0, NA) +
  labs(colour = "Reserve\nfraction") +
  theme_bw() +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white")#,
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.border = element_blank()
  )

#### Yield
yld_ts_plt <- bio_yield_sel_df %>%
  dplyr::filter(f_fmsy != 0) %>%
  ggplot(data = ., aes(x = year, y = rel_annual_yield)) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  geom_ribbon(aes(
    ymin = 1,
    ymax = pmin(rel_annual_yield, 1),
    fill = "Yield lower"
  )) +
  geom_ribbon(aes(
    ymin = rel_annual_yield,
    ymax = pmin(rel_annual_yield, 1),
    fill = "Yield higher"
  )) +
  geom_line(colour = "black") +
  geom_segment(aes(x = 1, y = 1, 
                     xend = 135, yend = 1),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 11000,
  #   aes(label = mean_biomass_lab)
  # ) +
  # geom_text(
  #   data = summary_stats_df,
  #   x = x_text_val,
  #   y = 12500,
  #   aes(label = sd_biomass_lab)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 14000,
#   aes(label = yrs_below_thresh)
# ) +
# geom_text(
#   data = summary_stats_df,
#   x = x_text_val,
#   y = 9500,
#   aes(label = cv_biomass_lab)
# ) +
labs(fill = "Above/Below Yield threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  # ylab("Yield (metric tons)") +
  ylab("Relative Yield") +
  ylim(0, NA) +
  labs(colour = "Reserve\nfraction") +
  theme_bw() +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white")#,
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.border = element_blank()
  )
# }

@@

### Figure 5 with text

```{r}
### Biomass

summary_stats_df_plot <- summary_stats_df[[2]] %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = as.numeric(reserve_frac), tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys, near, x = f_fmsy, tol = 1e-4
  ), `|`))

summary_stats_df_plot_yld <- summary_stats_df[[2]] %>%
  dplyr::filter(reduce(map(
    frac_reserves, near, x = as.numeric(reserve_frac), tol = 1e-4
  ), `|`)) %>%
  dplyr::filter(reduce(map(
    u_f_fmsys[-1], near, x = f_fmsy, tol = 1e-4
  ), `|`))

biom_ts_plt <- ggplot(
  bio_yield_sel_df %>% dplyr::filter(sim_num == sim_2_use),
  aes(x = year, y = rel_annual_biomass)
  # aes(x = year, y = annual_biomass)
) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  # geom_ribbon(aes(
  #   ymin = biomass_thresh,
  #   ymax = pmin(annual_biomass, biomass_thresh),
  #   fill = "Biomass lower"
  # )) +
    geom_ribbon(aes(
    ymin = 1,
    ymax = pmin(rel_annual_biomass, 1),
    fill = "Biomass lower"
  )) +
  # geom_ribbon(aes(
  #   ymin = annual_biomass,
  #   ymax = pmin(annual_biomass, biomass_thresh),
  #   fill = "Biomass higher"
  # )) +
    geom_ribbon(aes(
    ymin = rel_annual_biomass,
    ymax = pmin(rel_annual_biomass, 1),
    fill = "Biomass higher"
  )) +
  geom_line(colour = "black") +
    geom_segment(aes(x = 1, y = 1, 
                     xend = 135, yend = 1),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
geom_text(
  data = summary_stats_df_plot,
  x = x_text_val,
  # y = 11000,
  # aes(label = mean_biomass_lab)
  y = 3.4,
  size = 3,
  aes(label = mean_rel_biomass_lab)
) +
geom_text(
  data = summary_stats_df_plot,
  x = x_text_val,
  # y = 12500,
  # aes(label = sd_biomass_lab)
  y = 3.1,
  size = 3,
  aes(label = sd_rel_biomass_lab)
) +
geom_text(
  data = summary_stats_df_plot,
  x = x_text_val,
  # y = 14000,
  # aes(label = yrs_below_thresh)
  y = 2.8,
  size = 3,
  aes(label = yrs_below_biomass_thresh_lab)
) +
geom_text(
  data = summary_stats_df_plot,
  x = x_text_val,
  # y = 9500,
  # aes(label = cv_biomass_lab)  
  y = 2.5,
  size = 3,
  aes(label = cv_rel_biomass_lab)
) +
labs(fill = "Above/Below Biomass threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  # ylab("Biomass (metric tons)") +
  ylab("Relative Biomass") +
  ylim(0, NA) +
  labs(colour = "Reserve\nfraction") +
  theme_bw() +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white")#,
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.border = element_blank()
  )

#### Yield
# summary_stats_df_plot_yld

yld_ts_plt <- bio_yield_sel_df %>%
  dplyr::filter(f_fmsy != 0) %>%
  ggplot(data = ., aes(x = year, y = rel_annual_yield)) +
  facet_grid(reserve_frac ~ f_fmsy,
             labeller = labeller(f_fmsy = label_both,
                                 reserve_frac = label_both)) +
  geom_ribbon(aes(
    ymin = 1,
    ymax = pmin(rel_annual_yield, 1),
    fill = "Yield lower"
  )) +
  geom_ribbon(aes(
    ymin = rel_annual_yield,
    ymax = pmin(rel_annual_yield, 1),
    fill = "Yield higher"
  )) +
  geom_line(colour = "black") +
  geom_segment(aes(x = 1, y = 1, 
                     xend = 135, yend = 1),
             colour = "red",
             linewidth = 0.6) +
  scale_fill_manual(values = c("black", "grey80")) +
geom_text(
  # data = summary_stats_df,
  data = summary_stats_df_plot_yld,
  x = x_text_val,
  # y = 11000,
  # aes(label = mean_biomass_lab)
  y = 2.45,
  size = 3,
  aes(label = mean_biomass_lab)
) +
geom_text(
  # data = summary_stats_df,
  data = summary_stats_df_plot_yld,
  x = x_text_val,
  # y = 12500,
  # aes(label = sd_biomass_lab)
  y = 2.2,
  size = 3, 
  aes(label = sd_rel_yield_lab)
) +
geom_text(
  # data = summary_stats_df,
  data = summary_stats_df_plot_yld,
  x = x_text_val,
  # y = 14000,
  y = 1.95,
  size = 3,
  aes(label = yrs_below_yield_thresh_lab)
) +
geom_text(
  # data = summary_stats_df,
  data = summary_stats_df_plot_yld,
  x = x_text_val,
  # y = 9500,
  # aes(label = cv_yield_lab)
  y = 1.7,
  size = 3,
  aes(label = cv_rel_yield_lab)
) +
labs(fill = "Above/Below Yield threshold") +
  ggtitle(title_string) +
  xlab("Year") +
  # ylab("Yield (metric tons)") +
  ylab("Relative Yield") +
  ylim(0, 2.6) +
  labs(colour = "Reserve\nfraction") +
  theme_bw() +
  scale_x_continuous(expand = expansion(mult = 0, add = 0)) +
  theme(
    axis.line = element_line(colour = "black"),
    panel.background = element_rect(fill = "white")#,
    # panel.grid.major = element_blank(),
    # panel.grid.minor = element_blank(),
    # panel.border = element_blank()
  )
# }

ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries-text.png", plot = biom_ts_plt,
       height = 8, width = 14)
ggsave(filename = "output/tmp_figs/fig6-yield-timeseries-text.png", plot = yld_ts_plt,
       height = 8, width = 14)

ggsave(filename = "output/tmp_figs/fig5-biomass-timeseries-text.svg", plot = biom_ts_plt,
       height = 8, width = 14)
ggsave(filename = "output/tmp_figs/fig6-yield-timeseries-text.svg", plot = yld_ts_plt,
       height = 8, width = 14)
```

@@

med_biomass <- get_median_biomass(input_df = out_fs)

# White
# No dispersal
chr_nd_white_med_biomass <- get_median_biomass(input_df = chr_nd_white_out_fs) 
chr_nd_white_med_biomass
cab_nd_white_med_biomass <- get_median_biomass(input_df = cab_nd_white_out_fs) 
cab_nd_white_med_biomass
# larval pool dispersal 
chr_lp_white_med_biomass <- get_median_biomass(input_df = chr_lp_white_out_fs) 
chr_lp_white_med_biomass
cab_lp_white_med_biomass <- get_median_biomass(input_df = cab_lp_white_out_fs) 
cab_lp_white_med_biomass

# ENSO
# No dispersal
chr_nd_mei_med_biomass <- get_median_biomass(input_df = chr_nd_mei_out_fs) 
chr_nd_mei_med_biomass
cab_nd_mei_med_biomass <- get_median_biomass(input_df = cab_nd_mei_out_fs) 
cab_nd_mei_med_biomass
# larval pool dispersal
chr_lp_mei_med_biomass <- get_median_biomass(input_df = chr_lp_mei_out_fs) 
chr_lp_mei_med_biomass
cab_lp_mei_med_biomass <- get_median_biomass(input_df = cab_lp_mei_out_fs) 
cab_lp_mei_med_biomass

@@

chr_nd_white_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_white_out_fs)
cab_nd_white_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_white_out_fs)
chr_lp_white_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_white_out_fs)
cab_lp_white_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_white_out_fs)
chr_nd_mei_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_nd_mei_out_fs)
cab_nd_mei_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_nd_mei_out_fs)
chr_lp_mei_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = chr_lp_mei_out_fs)
cab_lp_mei_out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = cab_lp_mei_out_fs)
